Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
Note on stencil approximations

\subsubsection{A note on region approximations}

>>>>

\subsubsection{A note on stencil approximations}

As noted above, the \textsf{fivepoint} region defined above is more accepting
than that used in Section~\ref{sec:lang}. This introduces a new notion of
approximation beyond that is achieved in Section~\ref{sec:semantics}
using upper and lower bounds because the in both cases the specifications are
used to generate \emph{exact} models. Formally, we say a specification $s'$
approximates a more specific specification $s$ \emph{iff} $\forall m \in
\textsf{Mult}(\domainVal) . \mathit{cons}(s,m) \implies \mathit{cons}(s',m)$.

Equations provided on regions in Section~\ref{sec:lang} when all modifiers
equal provide such approximations, but it goes further than that. The
regions describing the fivepoint stencil for example cannot be shown equal
using these equations, but satisfies the approximation predicate as defined
above.

The checking algorithm though happily accepts an approximation in place of the
most specific specification. Although this decreases the likelihood of catching
stencil errors (as more access patterns conform), it reduces the space and
effort it takes to write the specification.
